Performance of Magnetic Refrigerators Operating with Different Magnetic Profiles

### 2019-09-02 PaperMagneticProfiles_JBSMSE.tex
Develop draft of introduction.

\begin{abstract}
 Magnetic refrigeration is a technology based on the concept of the active magnetic regenerator (AMR), which is a solid porous matrix of magnetocaloric material that undergoes temperature variations according to changes in the magnetization synchronized with oscillatory fluid flows. The magnetic field can be applied to the AMR in different profiles (waveforms). In this work, the performance of a magnetic refrigerator is evaluated in terms of two of the most common magnetic profiles: an instantaneous profile and a rectified cosine profile. The results show that the performance of an AMR operating with the instantaneous profile is consistently better than an AMR using the cosine profile with the same average high magnetic field and same minimum value, and that this improvement is higher for larger utilizations (ratio of solid to fluid thermal capacities). For an AMR frequency of \SI{1}{\hertz} and an utilization of 1.0, the cooling capacity of an AMR device operating with the instantaneous profile was \SI{196.3}{\percent} higher than the equivalent rectified cosine profile. The instantaneous profile was then analyzed in more detail, and it was concluded that using high values of magnetic field allows for smaller regenerators and lower mass flow rates to keep a desired level of cooling power.

@@

\section{INTRODUCTION}
\label{sec:introduction}

An active magnetic regenerator (AMR)  is a thermal regenerator composed of a solid porous matrix of magnetocaloric material, which changes its temperature according to the application of a varying magnetic field in synchronization with oscillatory fluid flows, due to the so-called magnetocaloric effect (MCE). Active magnetic regenerators are employed in magnetic refrigeration, a promising alternative to vapor compression systems due to its use of non-gaseous refrigerants and potentially higher  thermodynamic efficiency \cite{bib:trevizoli}. A magnetic refrigerator may contain multiple regenerator beds, in combination with rotary permanent magnets, to achieve higher levels of performance \cite{bib:trevizoli16_pump}.

The time variation of the magnetic field experienced by an AMR is known as the magnetic profile. The magnetic profile is directly related to the thermodynamic cycle that drives the magnetic refrigerator, and therefore has an important influence on its performance. AMRs can operate according to different thermodynamic cycles, but the most common is the Brayton AMR cycle, which has two isentropic processes of instantaneous magnetization and demagnetization of the magnetocaloric material and two isofield processes \cite{bib:kitanovski}, as shown in Fig.~\ref{fig:brayton}. In practice, it is difficult to generate  stepwise variations of the magnetic field (as required by  the Brayton cycle) using permanent magnets arrays (the apparently only viable solution for domestic magnetic refrigerators due to low cooling requirements and energy consumption). Most magnetic refrigerators developed so far operate with a more continuous magnetic profile, such as the rectified cosine profile \cite{bib:tura-rowe-amr,bib:arnold14_desig,bib:trevizoli15_desig_halbac}, which is easily generated with compact devices and capable of achieving high levels of magnetic field \cite{bib:trevizoli16_pump}, but at the cost of  too brief demagnetization periods.

\begin{figure}[!ht]
  \centering
%  \includegraphics[width=5cm]{brayton-kitanovski}
  \caption{Temperature-entropy diagram for the Brayton AMR cycle, as experienced by the magnetocaloric (MC)  material \cite{bib:kitanovski}. The applied magnetic field is denoted by $H$.}
  \label{fig:brayton}
\end{figure}

In Fig.~\ref{fig:cycles}, the instantaneous and rectified cosine waveforms evaluated in this work are shown in terms of the average applied magnetic field ($\average{B}$) that acts on the regenerator (vertical axis) for one AMR cycle parameterized in a time variable ($t$) ranging from 0 to the cycle period $\tau$ (horizontal axis).

\begin{figure}[!ht]
  \centering
  \includegraphics[width=7cm]{profiles.jpg}
  \caption{Instantaneous and rectified cosine magnetic profiles in terms of the average magnetic field over the regenerator for one AMR cycle as a function of time ($t$). }
  \label{fig:cycles}
\end{figure}

Besides the applied magnetic field variations shown in Fig.~\ref{fig:cycles}, an AMR cycle is also composed of two hydraulic processes: (i) cold blow, occurring after the magnetization, where cold fluid flows through the porous matrix to absorb energy from it and rejects heat to an external hot source, and (ii) hot blow, occurring after the demagnetization, where the magnetocaloric material is cooled down and removes heat from the fluid flowing, which then can absorb the thermal load from the cold source.

Many works on the analysis of  magnetic profiles used a ramp profile as  an approximation of the instantaneous profile with finite transition times between the magnetization levels, making it easier to generate the profiles with permanent magnets. The performance of an AMR subjected to a ramp profile with different parameters was performed by \cite{bib:bjoerk11_amr}, but the emphasis was on the synchronization with the fluid flow profile and the authors did not compare different magnetic profiles. The previously cited investigation by \cite{bib:kitanovski} implemented different cycles through a ramp profile and a modification of the rectified cosine (consisting only of linear variations), and concluded that, with the same operating parameters parameters (temperature span between heat source and heat sink, frequency, mass flow rate, regenerator geometry, maximum applied magnetic field), the Brayton cycle (realized by a ramp profile) results in the highest cooling capacities; the same profile could be used in Ericsson cycles, with the magnetization processes done isothermally instead of adiabatically, and the result is higher values of the coefficient of performance. A comparison of different magnetic profiles for an AMR device was also performed by \cite{bib:asme-mce}, and  the authors concluded that, for same levels of maximum and minimum magnetic field, the instantaneous profile results in higher cooling capacities for a given temperature span.

The present work extends these analyses and attempts to systematically compare the performance of a magnetic refrigerator operating with instantaneous and  rectified cosine profiles under different parameters, with the goal of selecting the best magnetic profile for certain requirements of cooling capacity of a target application. In comparison with the previously cited works, we analyze the effect of different regenerator geometries and different levels of the magnetic field and mass flow rate. In particular, in comparison with the work of \cite{bib:kitanovski}, where the authors studied different combinations of flow and magnetic profiles to yield various thermodynamic cycles, we fix the fluid flow profile to better investigate the effect of the magnetic profile, which is used in the design of magnetic circuits.

@@

\bibliography{thermo-ref/Thermo-Foam-Ref}

>>>>

\begin{abstract}

@@

\section{Introduction}
\label{sec:introduction}

An active magnetic regenerator (AMR)  is a thermal regenerator composed of a solid porous matrix of magnetocaloric material, which changes its temperature according to the application of a varying magnetic field in synchronization with oscillatory fluid flows, due to the so-called magnetocaloric effect (MCE). Active magnetic regenerators are employed in magnetic refrigeration, a promising alternative to vapor compression systems due to its use of non-gaseous refrigerants and potentially higher  thermodynamic efficiency \cite{bib:trevizoli}. A magnetic refrigerator may contain multiple regenerator beds, in combination with rotary permanent magnets, to achieve higher levels of performance \cite{bib:trevizoli16_pump}. Since the working fluid only has energy transport functions and does not change its phase, aqueous solutions with freezing and corrosion inhibitors are usually employed.

The dynamic nature of AMR systems are described by two characteristic waveforms:

\begin{enumerate}
\item The \emph{magnetic profile}, which describes the time variation of the magnetic field experienced by the regenerators;
\item The \emph{fluid flow profile}, which describes the oscillatory flow rate though the regenerators
\end{enumerate}

Different combinations and arrangements of these waveforms yield different thermodynamic cycles through which an AMR system can operate. The most common cycle in the literature is the Brayton AMR cycle, which has two isentropic processes of instantaneous magnetization and demagnetization of the magnetocaloric material and two isofield processes \cite{bib:kitanovski}, as shown in Fig.~\ref{fig:brayton}. During magnetization, the solid material warms up due to the MCE; with a constant applied magnetic field, fluid flows, absorbing this energy and releasing it in the hot heat exchanger; the magnetic field is changed to a low level, cooling down the material; fluid from the hot source flows through the bed, releases its energy to the material, and the cold fluid can then absorb heat from the cold source.

\begin{figure}[!ht]
  \centering
 %\includegraphics[width=5cm]{brayton-kitanovski}
  \caption{Temperature-entropy diagram for the Brayton AMR cycle, as experienced by the magnetocaloric (MC)  material \cite{bib:kitanovski}. The applied magnetic field is denoted by $H$.}
  \label{fig:brayton}
\end{figure}

The performance of AMR-based magnetic refrigerators is directly related to their thermodynamic cycle, and hence to the magnetic and fluid flow profiles. With this motivation, there are multiple studies in the literature regarding these waveforms. In general, the fluid flow profile is more easily changed in experimental prototypes with modifications in the hydraulic system, and it can be optimized for a given magnetic profile for higher cooling capacity or coefficient of performance \cite{bib:teyber17_exper,bib:nakashima18-influen-exp,FORTKAMP2018}. The actual shape of waveform depends on the hydraulic system configuration; single- or two-regenerators systems usually employ piston pumps with sinusoidal fluid flow profiles, while more complex valving system yield trapezoidal fluid flow profiles, with periods of no flow (when fluid is by-passed from the regenerator), periods with a constant flow rate and ramp transitions between these two states.

In room temperature magnetic refrigeration, the magnetic profile is generated by permanent magnets, representing the most expensive part of a magnetic refrigerator \cite{bib:bjoerk16_lifetime}, and hence considered fixed in AMR devices. Although the magnetic profile can be changed with motion control on the permanent magnets \cite{bib:benedict16_desig}, this is a topic yet to be better investigated, and most studies on the subject are numerical. The ideal Brayton cycle requires a instantaneous magnetic profile (square waveform), but in practice it is difficult to generate  stepwise variations of the magnetic field  using rotating permanent magnets arrays. Most magnetic refrigerators developed so far operate with a more continuous magnetic profile, such as the rectified cosine profile \cite{bib:tura-rowe-amr,bib:arnold14_desig,bib:trevizoli15_desig_halbac}, which is easily generated with compact devices and capable of achieving high levels of magnetic field \cite{bib:trevizoli16_pump}, but at the cost of  too brief demagnetization periods.

Many works on the analysis of  magnetic profiles use a ramp profile as  an approximation of the instantaneous profile with finite transition times between the magnetization levels, making it easier to generate the profiles with permanent magnets. The performance of an AMR subjected to a ramp magnetic profile and a instantaneous fluid flow profile with different parameters has been investigate \cite{bib:bjoerk11_amr}, but the emphasis was on the synchronization with the fluid flow profile and the authors did not compare different magnetic profiles. A study that  implemented different cycles through a ramp profile and a modification of the rectified cosine (consisting only of linear variations) \cite{bib:kitanovski} concluded that, with the same operating parameters parameters (temperature span between heat source and heat sink, frequency, mass flow rate, regenerator geometry, maximum applied magnetic field), the Brayton cycle (realized by a ramp profile) results in the highest cooling capacities; the same profile could be used in Ericsson cycles, with the magnetization processes done isothermally instead of adiabatically, and the result is higher values of the coefficient of performance. The conclusion that the instantaneous magnetic profile results in higher cooling capacities for a given temperature span, compared to other waveforms is also presented in \cite{bib:asme-mce}

In Fig.~\ref{fig:cycles}, the instantaneous and rectified cosine waveforms evaluated in this work are shown in terms of the average applied magnetic field (${B}$) that acts on the regenerator (vertical axis) for one AMR cycle parameterized in a time variable ($t$) ranging from 0 to the cycle period $\tau$ (horizontal axis).

\begin{figure}[!ht]
  \centering
  \includegraphics[width=7cm]{profiles_all.eps}
  \caption{Instantaneous and rectified cosine magnetic profiles in terms of the average magnetic field over the regenerator for one AMR cycle as a function of time ($t$). }
  \label{fig:cycles}
\end{figure}

The present work extends these analyses and attempts to systematically compare the performance of a magnetic refrigerator operating with instantaneous, rectified cosine and ramp magnetic  profiles under different parameters, with the goal of selecting the best magnetic profile for certain requirements of cooling capacity of a target application. In comparison with the previously cited works, we analyze the effect of different regenerator geometries and different levels of the magnetic field and mass flow rate. In particular, in comparison with the work of \cite{bib:kitanovski}, where the authors studied different combinations of flow and magnetic profiles to yield various thermodynamic cycles, we fix the fluid flow profile to better investigate the effect of the magnetic profile, which is used in the design of magnetic circuits.

@@

\bibliography{thermo-ref/Thermo-Foam-Ref,thermo-ref/thesis}
